Heterogeneity in pregregistered multi-lab studies

### 2018-03-02 code/heterogeneity.rmd
Standardized RRR8

@@

    fit2 <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives Hedge's g as outcome
               n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){  #this currently gives us the estimate for the raw effect, but with SE should be possible to back-transform to smd

    fit <- fit2 <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x)

    I2_1 <- rep(NA, 3)
    I2_2 <- confint(fit2)$random[3, ]
    #In this case, stop function and return dataframe below
    return(data.frame(s_I2 = I2_1[1], s_ci.lb = I2_1[2], s_ci.ub = I2_1[3], r_I2 = I2_2[1], r_ci.lb = I2_2[2], r_ci.ub = I2_2[3])) #output is for smd, r, and 1 raw difference

@@

    fit <- rma(measure = "OR2D", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #transformed to smd
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

    fit2 <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #transformed to smd
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
  }

@@

```
**Note**: NA in unstandardized columns comes from correlations which I don't think is possible to calculate the unstandardized version for with the available information. RRR5 I have not yet been able to extract a measure of variance for, hence the NAs. RRR8 I only have the SE for the raw mean difference and have yet to figure out how use this to estimate a standardized effect.

>>>>

#this function is for transforming RRR8 which only has raw mean difference and SE to a standardized version
transform_SE <- function(ES, SE, n1, n2){ #Based on meta-analysis lecture 02
  sdpooled <- sqrt(SE^2 / (1 / n1 + 1/n2))
  d <- ES / sdpooled
  g <- (1 - 3 / (4*(n1 + n2) - 9))*d
  v <- 1 / n1 + 1/ n2 + g^2 / (2*(n1 + n2))
  data.frame(g = g, v = v)
}

@@

    fit2 <- rma(measure = "MD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, #gives raw outcome
               n1i = ntreatment, n2i = ncontrol,test = "knha", data = x)

  } else if(any(x[, "outcomes1_2"] == "mean _ SE")){

    standardized <- transform_SE(x$effect_size, x$outcome_c2, x$ntreatment, x$ncontrol)

    fit <- rma(yi = g, vi = v, test = "knha", data = standardized) #standardized effect estimate

    fit2 <-  rma(yi = effect_size, sei = outcome_c2, test = "knha",  data = x) #raw effect estimate

@@

    fit <- rma(measure = "OR2D", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #standardized
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)

    fit2 <- rma(measure = "RD", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, #unstandardized
               n1i = ntreatment, n2i = ncontrol, test = "knha", data = x)
  }

@@

```
**Note**: I am uncertain if we can speak of standardized/unstandardized in regards to 2x2 tables? For now these correspond to OR/Risk difference for the following five effects {Allowed vs forbidden, gain vs. loss framing, norm of reciprocity, low vs. high category scale, verbal overshadowing}. NA in unstandardized columns comes from correlations which don't seem possible to calculate the unstandardized version for with the available information. RRR5 I have not yet been able to extract a measure of variance for, hence the NAs.
